Breeding bird indicators

### 2023-10-24 DRAFT_birdIndicators.Rmd
Removed one eval = FALSE that prevented Trim_data download
Added sentence on specification of database driver

#### Monitoring data from "Hekkefuglovervåkingen"
The route-based raw data from "hekkefuglovervåkingen" are compiled after each breeding season and stored in NINA's database. From that database we download the data relevant for the PECBMS Trim analyses and for the specified range of years (here from 2006 up to and including 2022).

```{r, eval = FALSE}
minYear <- 2006
maxYear <- 2022

>>>>

#### Monitoring data from "Hekkefuglovervåkingen"
The route-based raw data from "hekkefuglovervåkingen" are compiled after each breeding season and stored in NINA's database. From that database we download the data relevant for the PECBMS Trim analyses and for the specified range of years (here from 2006 up to and including 2022). The function ``downloadData_TRIM`` does that for a specified year range (from ``minYear`` up to and including ``maxYear``), and requires specifying which driver is used for accessing the database (via argument ``DriverName``). When running from the NINA RStudio server, we need to use "FreeTDS". When running locally from NINA computers, we need to select "SQL Server".

```{r}
minYear <- 2006
maxYear <- 2022
